---
title: "Airbnb Project"
author: "Helen Zhou"
date: "11/26/2017"
output: pdf_document
---

```{r setup, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggthemes)
library(ggplot2)
require(gridExtra)
library(lme4)
```

## Midterm Project_Airbnb

This project is designed to display data analysis based on Inside Airbnb data set from http://insideairbnb.com/get-the-data.html. Datas contain two cities: Boston and New York City. For each city, I use property listing data.

The model I built is mainly focused on the price prediction. 

The major procedure can be summarized as below:
1. Data Reading and Preparation
2. EDA
4. Multi-level linear model 
5. Reference and appendix 

```{r echo=FALSE }
# Data from Boston
bos_list <- read.csv("listingsBOS.csv") 
bos_list_sum <- read.csv("listings_sumBOS.csv")
#bos_review <- read.csv("reviewsBOS.csv")
# Data from New York City
nyc_list <- read.csv("listingsNYC.csv") 
nyc_list_sum <- read.csv("listings_sumNYC.csv")
#nyc_review <- read.csv("reviewsNYC.csv")
```

```{r echo=FALSE }
# Data preparation
# Bos_list_sum is a simplified version of Bos_list, and I added some info from bos_list to bos_list_sum and use the later one for the analysis
bos_list[,c("listing_url","scrape_id","last_scraped","space","description","experiences_offered","neighborhood_overview","notes",
            "transit","access","interaction","house_rules","thumbnail_url","medium_url","picture_url",
            "xl_picture_url","host_id","host_url","host_thumbnail_url","host_picture_url", "host_listings_count",
            "neighbourhood_group_cleansed","require_guest_profile_picture","require_guest_phone_verification" )] <- list(NULL)
#bos_list <- bos_list[complete.cases(bos_list), ]
#drop unneccesary columns 
nyc_list[,c("listing_url","scrape_id","last_scraped","space","description","experiences_offered","neighborhood_overview","notes",
            "transit","access","interaction","house_rules","thumbnail_url","medium_url","picture_url",
            "xl_picture_url","host_id","host_url","host_thumbnail_url","host_picture_url", "host_listings_count",
            "neighbourhood_group_cleansed","require_guest_profile_picture","require_guest_phone_verification" )] <- list(NULL)
#nyc_list <- nyc_list[complete.cases(nyc_list), ]
```

# EDA and second round data cleaning

To find out people's experience with Airbnb in one city, we first need to know what are the options there 

```{r echo=FALSE }
#distribution of property type - BOS
library(plyr)
y <- count(bos_list, 'property_type')
p <- ggplot(y, aes(x=reorder(property_type,-freq),y = freq, fill = factor(property_type))) 
p + geom_bar(stat = "identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + ggtitle("Property Type Distribution in Boston") + labs(x="Property Type",y="Count")
#distribution of property type- NYC
y <- count(nyc_list, 'property_type')
p <- ggplot(y, aes(x=reorder(property_type,-freq),y = freq, fill = factor(property_type))) 
p + geom_bar(stat = "identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + ggtitle("Property Type Distribution in NYC") + labs(x="Property Type",y="Count") 
detach(package:plyr)
```

```{r echo=FALSE }
#distribution of room type - BOS
p <- ggplot(data=bos_list, aes(x=factor(1), fill = factor(room_type)),) + geom_bar(width = 1)
pp1 <- p + coord_polar(theta = "y") + ggtitle("Room Type Distribution in Boston") + labs(x="Room Type",y="Count") + theme(plot.title = element_text(size=15))
#distribution of room type - NYC
p <- ggplot(data=nyc_list, aes(x=factor(1), fill = factor(room_type)),) + geom_bar(width = 1)
pp2 <- p + coord_polar(theta = "y") + ggtitle("Room Type Distribution in NYC") + labs(x="Room Type",y="Count") + theme(plot.title = element_text(size=15))
grid.arrange(pp1, pp2, ncol=2)
```

```{r warning=FALSE, message=FALSE,echo=FALSE }
#distribution of neighborhood - BOS
library(ggmap)
df <- (data.frame(
  x = bos_list$latitude,
  y = bos_list$longitude,
  Type = bos_list$room_type
))
ppp1 <- qmplot(y, x, data = df, colour = Type, size = I(0.1), darken = 0) + ggtitle("Property Distribution in Boston")

#get_map(location = c(lon = df$y, lat = df$x), zoom = "auto", scale = "auto", maptype = "roadmap", source = "google", force = ifelse(source == "google", TRUE, TRUE), messaging = FALSE, urlonly = FALSE, filename = "ggmapTemp", crop = TRUE, color = c("color", "bw"), language = "en-EN", api_key)

#distribution of neighborhood - NYC
df <- (data.frame(
  x = nyc_list$latitude,
  y = nyc_list$longitude,
  Type = nyc_list$room_type
))
ppp2 <- qmplot(y, x, data = df, colour = Type, size = I(0.1), darken = 0) + ggtitle("Property Distribution in NYC")
grid.arrange(ppp1, ppp2, ncol=2)
```

```{r warning=FALSE, message=FALSE,echo=FALSE }
#wordcloud - BOS
library(tm)
library(SnowballC)
library(wordcloud)
bos_sum <- read.csv("listings_sumBOS.csv", stringsAsFactors = FALSE)
bosCorpus <- Corpus(VectorSource(bos_sum$name))
bosCorpus <- tm_map(bosCorpus, PlainTextDocument)
bosCorpus <- tm_map(bosCorpus, removePunctuation)
bosCorpus <- tm_map(bosCorpus, removeWords, stopwords('english'))
bosCorpus <- tm_map(bosCorpus, stemDocument)
bosCorpus <- tm_map(bosCorpus, removeNumbers)
bosCorpus <- tm_map(bosCorpus, stripWhitespace)
bosCorpus <- tm_map(bosCorpus, tolower)
bosCorpus <- tm_map(bosCorpus, removeWords, "bedroom")
bosCorpus <- tm_map(bosCorpus, removeWords, "room")
wordcloud(bosCorpus, max.words = 100, random.order = FALSE,colors = brewer.pal(9,"Reds"))
#layout(matrix(c(1,1,2,3), 2, 2, byrow = TRUE))
#wordcloud - NYC
nyc_sum <- read.csv("listings_sumNYC.csv", stringsAsFactors = FALSE)
nycCorpus <- Corpus(VectorSource(nyc_sum$name))
nycCorpus <- tm_map(nycCorpus, PlainTextDocument)
nycCorpus <- tm_map(nycCorpus, removePunctuation)
nycCorpus <- tm_map(nycCorpus, removeWords, stopwords('english'))
nycCorpus <- tm_map(nycCorpus, stemDocument)
nycCorpus <- tm_map(nycCorpus, removeNumbers)
nycCorpus <- tm_map(nycCorpus, stripWhitespace)
nycCorpus <- tm_map(nycCorpus, tolower)
nycCorpus <- tm_map(nycCorpus, removeWords, "bedroom")
nycCorpus <- tm_map(nycCorpus, removeWords, "room")
wordcloud(nycCorpus, max.words = 100, random.order = FALSE,colors = brewer.pal(9,"Blues"))

```

```{r eval=FALSE}
# distribution of price - BOS
qplot(bos_list$price,geom="histogram",binwidth = 0.5,  main = "Histogram for Price in Boston", xlab = "Price",  fill=I("blue"), col=I("red"), alpha=I(.2),stat = "count")
p + coord_polar(theta = "y")
# distribution of price - NYC
```

# Model and model visualization

I fit a multi-level model for each city. 

$$y_i^{price} = \mu + \gamma_{1}^{room type} + \delta^{neighbourhood}  + e_i$$

```{r}
# Multi-level model
# Boston 
m1 <- lmer(formula = price ~ 1 + (1 | room_type) + (1 | neighbourhood), data = bos_list_sum)
# New York 
m2 <- lmer(formula = price ~ 1 + (1 | room_type) + (1 | neighbourhood), data = nyc_list_sum)
```

```{r echo=FALSE }
# residual plot 
a1 <- plot(m1, main = "residual plot Boston")
a2 <- plot(m2, main = "residual plot NYC")
grid.arrange(a1, a2, ncol=2)
```



